Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-13 journal/content.tex
Statements on contribution

A particular problem in this systematic literature review was the limitations of
Boolean keyword searches in online databases. A keyword search can not identify
the facet of \emph{large scale}, and also \emph{transformation} is difficult to
capture with keywords. Because of this we assume that it is likely that a some
studies have been missed by the keyword search, potentially causing bias. To
eliminate the potential bias we would suggest manually searching the entire
archive of \emph{Agile Conference} and \emph{Agile Processes in Software
Engineering and Extreme Programming} for relevant studies. These two conferences
provided more than two thirds of the primary sources.

@@

\newpage
\section{Conclusion}

The goal of this work was to review and analyze empirical studies of large
organizations taking agile software development methods into use. By applying
the method of systematic literature review we analyzed the findings of 52
studies describing the agile transformation in 42 different organizations. As a
result we presented qualitative findings describing typical reasons to change,
characteristics of transformations, challenges, and success factors.

>>>>

A particular problem in this systematic literature review was the limitations of
Boolean keyword searches in online databases. A keyword search can not identify
the facet of \emph{large scale}, and also \emph{transformation} is difficult to
capture with keywords. Because of this we assume that it is likely that a some
studies have been missed by the keyword search, potentially causing bias. To
eliminate the potential bias we would suggest manually searching the entire
archive of \emph{Agile Conference} and \emph{International conference on agile
software development} (also known as XP conference) for relevant studies.
% XP = Agile Processes in Software Engineering and Extreme Programming
These two conferences provided more than two thirds of the primary sources.

@@

\section{Conclusion}

This work makes a unique contribution on a topical area in research on agile
software development. In the past decade there has been numerous publications
discussing use of agile in large scale organizations. However, the process of
adopting agile in large organizations has not been studied extensively before.
Numerous experience reports and case studies discussing large agile adoptions
exist, but there is a lack of aggregating work providing an overview of this
subject area.
This work presents a unique compilation and summarizing analysis of existing
publications on large scale agile adoptions.

The systematic literature review method creates solid evidence that can act as
background for further research.
For practitioners the results provide an extensive collection of viewpoints to
consider in an adoption process, and the primary sources act as a listing of
cases to compare against.

The goal of this work was to review and analyze empirical studies of large
organizations taking agile software development methods into use. By applying
the method of systematic literature review we analyzed the findings of 52
studies describing 42 different organizations adopting agile methods. As a
result we presented qualitative findings describing typical reasons to change,
characteristics of transformations, challenges, and success factors.
